The title

### 2019-06-17 analysis/paper/Chr13-prelim.Rmd
added Rmd files for initial analyses - mediation v pleiotropy test statistic

---
title: "Chr11 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 11
run_num <- 9921
hot_mid <- 71
```

>>>>

---
title: "Chr13 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 13
run_num <- 9931
hot_mid <- 112.5
```

### 2019-06-17 analysis/paper/Chr2-prelim.Rmd
added Rmd files for initial analyses - mediation v pleiotropy test statistic

---
title: "Chr13 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 13
run_num <- 9931
hot_mid <- 112.5
```

>>>>

---
title: "Chr2 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 2
run_num <- 9941
hot_mid <- 165.5
```

### 2019-06-17 analysis/paper/Chr7-prelim.Rmd
added Rmd files for initial analyses - mediation v pleiotropy test statistic

---
title: "Chr2 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 2
run_num <- 9941
hot_mid <- 165.5
```

>>>>

---
title: "Chr7 hotspot preliminary analyses"
author: "Frederick Boehm"
date: "6/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
hot_chr <- 7
run_num <- 9911
hot_mid <- 46
```

### 2019-06-17 analysis/paper/find-missing-jobs-chtc.Rmd
added Rmd files for initial analyses - mediation v pleiotropy test statistic

```{r}
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9901", njobs = 6734, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9901-bad")
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9911", njobs = 8979, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9911-bad")
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9921", njobs = 10332, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9921-bad")
```

>>>>

```{r, eval = TRUE}
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9901", njobs = 6734, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9901-bad")
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9911", njobs = 8979, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9911-bad")
find_missing_jobs(DIR = "~/Box Sync/attie/keller-hotspots/results/pvl-run-9921", njobs = 10332, outfile = "~/Box Sync/attie/keller-hotspots/submit_files/run9921-bad")
```

### 2019-06-17 analysis/paper/paper.Rmd
removed Marwick citation
added Rmd files for initial analyses - mediation v pleiotropy test statistic

Here is a citation [@Marwick2017]

@@

@@

```{r demo, eval = FALSE}
1 + 1
```

@@

@@

```{r}
install.packages("here", repos = "https://cloud.r-project.org")
```

>>>>

@@

@chick2016defining

@@

@@

@keller2018genetic studied gene expression in pancreatic islets of 378 Diversity Outbred mice. They used RNA sequencing technology to quantify 21,771 distinct transcripts. They publicly shared these data at this url.

We performed pleiotropy tests and mediation analyses at each of five hotspots that @keller2018genetic identified. They are located on Chromosomes 2, 5, 7, 11, and 13 .

@@

## Chr 2 hotspot

## Chr 5 hotspot

## Chr 7 hotspot

## Chr 11 hotspot

## Chr 13 hotspot

### 2019-06-17 paper.tex
added Rmd files for initial analyses - mediation v pleiotropy test statistic

\documentclass[oneside]{book}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
%\linenumbers

@@

%% end from vignette tex file

\begin{document}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE, echo = FALSE, fig.lp = "fig:", warning = FALSE, message = FALSE, results = "hide"
)
@

@@

<<load-broman>>=
library(broman)
@

@@

<<r install_here>>=
install.packages("here", repos = "https://cloud.r-project.org")
@

@@

<<r colophon, cache = FALSE>>=
# which R packages and versions?
devtools::session_info()
@

@@

<<r git2r, cache = FALSE>>=
# what commit is this file at?
git2r::repository(here::here())
@

>>>>

\documentclass[oneside]{book}\usepackage[]{graphicx}\usepackage[]{color}
% maxwidth is the original width if it is less than linewidth
% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
%\usepackage{lineno}
%\linenumbers

@@

%% end from vignette tex file
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

@@

@@

@@
